---
title       : Building a Data Product
subtitle    : With Shiny
author      : Pierre
job         : 2018-11-11
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
output      : ioslides_presentation
---

## K-Means clustering

When looking at uncategorised data, it can be useful to group similar observations together

 - K-Means clustering allows us to do just that
 - But finding the 'right' number of clusters can be a little tricky

This Shiny app enables the user to select a range of clusters, e.g. between 2 and 5, and run K-Means for each sample size (`2,3,4,5` in that case). The outputs will provide guidance as to the optimal number of clusters

## The app (1)

The output will be 2 graphs - one to visualise the clustering when plotting petal length vs petal width:

```{r kmeans, echo=FALSE}
suppressPackageStartupMessages({library(ggplot2)})
library(ggplot2)
library(grid)
library(gridExtra)
data(iris)
vals <- lapply(seq(2,5), function(k) {kmeans(iris[,3:4], k)})
plots <- lapply(vals, function(km) {
      km$cluster <- as.factor(km$cluster)
      num_clusters <- length(levels(km$cluster))
      ggplot(iris, aes(Petal.Length, Petal.Width, color = km$cluster)) + 
        geom_point() + ggtitle(paste(num_clusters,"cluster(s)", sep=" ")) +
        theme(legend.title=element_blank()) # remove the legend
    })
grid.arrange(grobs=plots, ncol=2)
```

## The app (2)

And another showing the total sum of squares within for each value of `k`:

```{r wss, echo=FALSE}
wss <- lapply(vals, function(km) {km$tot.withinss})
df <- data.frame(k=as.numeric(seq(2,5)),wss=as.numeric(wss))
ggplot(df, aes(x=k, y=wss)) + geom_line() + labs(x="Number of clusters", y="Within sum of squares", title="Sum of Squares within by number of clusters")
```

We will be using the `iris` dataset as an example (which happens to be categorised, so we know what the correct number of clusters should be)

## Final thoughts

- The `iris` dataset is actually categorised (there are 3 species)
- Due to the size of the dataset, it is relatively fast to run k-means
- The hardest part was figuring out how to dynamically add multiple plots to a single output

<center>
Thanks for watching!
</center>