---
title       : Fun with Slidify
subtitle    : R and slidify, the dynamic duo
author      : Pierre - 2018-10-28
job         : 2018-10-28
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
output: ioslides_presentation
---

## Data

In this short presentation we look at the seasonality of outbreaks of the Hand, Foot Mouth Disease in Singapore.

It is a disease that impacts many children every year.

The `data.gov.sg` initiative makes data available (
https://data.gov.sg/dataset/weekly-infectious-disease-bulletin-cases)

```{r d}
data <- read.csv("weekly-infectious-disease-bulletin-cases.csv")
library(dplyr)
library(tidyr)
hfmd <- data  %>%
        filter(disease == 'Hand, Foot Mouth Disease') %>%
        select(epi_week, no._of_cases) %>%
        separate(epi_week, c('year','week'), sep='-')
```

## Graph

```{r, echo=FALSE}
library(plotly)
suppressPackageStartupMessages({library(plotly)}) 
pl <- plot_ly(data=hfmd, x = ~week, y = ~no._of_cases, color=~year, type = 'scatter', mode='lines') %>%
      layout(xaxis=list(title='Weeks'), yaxis=list(title='Number of cases'), title='HFMD Outbreaks over the years')
pl
```

## Notes

- Getting `slidify` to play nice with `plot_ly` wasn't straightforward
- The trick was to set `output: ioslides_presentation` in the header
- And then call `rmarkdown::render("index.Rmd")`

## Thanks

<center>
That's all!
</center>